Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-21 paper.tex
change S to tau and delta t_out in equations

\begin{equation}
    N_{wasted}(t) = \sum\limits_{r \in R_t} \left(H[t-S_{sched}(t,r)] \cdot [1-O(t,r)]  \sum\limits_{t'=F_{prev}(t,r)}^{t} N_b(t',r) \right)
    \label{eq:badshare}
\end{equation}
%% What is the value of this function during a normal refueling outage,
%% immediately before S_(sched)(t)?  It seems you need another Heavyside
%% function to drop this back down to an expected value of 0 again.
%%
%%          ___________________
%%          |                 |
%%  ________|                 |_____________

where $R_t$ is the set of all reactors, $H$ is the Heaviside function,
$S_{sched}(t,r)$ is the original scheduled startup time of reactor $r$ after
the most recent refueling outage that started before $t$, $F_{prev}(t,r)$ is
the start of the most recent refueling outage for reactor $r$ before or on
time $t$, $O(t,r)$ is 1 if reactor $r$ is producing power at time $t$ and zero
otherwise, and $N_b(t,r)$ is the number of new fuel batches received by
reactor $r$ since time $t$.

@@

\begin{equation}
    P_{outage}(t) = \sum\limits_{r \in R_t} C_r \cdot H[t-S_{sched}(t,r)] \cdot [1-O(t,r)]
    \label{eq:shortage}
\end{equation}

where $R_t$ is the set of all reactors, $C_r$ is the power capacity of reactor
$r$, $H$ is the Heaviside function, $S_{sched}(t,r)$ is the original scheduled
startup time of reactor $r$ after the most recent refueling outage that
started before $t$, and $O(t,r)$ is 1 if reactor $r$ is producing power at
time $t$ and zero otherwise.

>>>>

\begin{equation}
    N_{wasted}(t) = \sum\limits_{r \in R_t} \left(H[t-(\tau(t,r) + \Delta\;t_{out})] \cdot [1-O(t,r)]  \sum\limits_{t'=F_{prev}(t,r)}^{t} N_b(t',r) \right)
    \label{eq:badshare}
\end{equation}
%% What is the value of this function during a normal refueling outage,
%% immediately before S_(sched)(t)?  It seems you need another Heavyside
%% function to drop this back down to an expected value of 0 again.
%%
%%          ___________________
%%          |                 |
%%  ________|                 |_____________

where $R_t$ is the set of all reactors, $H$ is the Heaviside function,
$\tau(t,r)$ is the beginning of the most recent refueling outage of reactor $r$ before $t$,
$\Delta\; t_{out}$ is the normal refueling outage duration, $F_{prev}(t,r)$ is
the start of the most recent refueling outage for reactor $r$ before or on
time $t$, $O(t,r)$ is 1 if reactor $r$ is producing power at time $t$ and zero
otherwise, and $N_b(t,r)$ is the number of new fuel batches received by
reactor $r$ since time $t$.

@@

\begin{equation}
    P_{outage}(t) = \sum\limits_{r \in R_t} C_r \cdot H[t-(\tau(t,r) + \Delta\;t_{out})] \cdot [1-O(t,r)]
    \label{eq:shortage}
\end{equation}

where $R_t$ is the set of all reactors, $C_r$ is the power capacity of reactor
$r$, $H$ is the Heaviside function, $\tau(t,r)$ is the beginning of the most
recent refueling outage of reactor $r$ before $t$, $\Delta\; t_{out}$ is the
normal refueling outage duration, and $O(t,r)$ is 1 if reactor $r$ is
producing power at time $t$ and zero otherwise.
